%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://mitulsavani.com/}{\Large Mitul Savani}} \\ 
  \href{mailto:mitul.savani1@gmail.com}{mitul.savani1@gmail.com} & \href{https://mitulsavani.github.io/}{Portfolio: mitulsavani.com} \\
  415-734-1688 & {\href{https://github.com/mitulsavani}{github.com/mitulsavani}} \\ 
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Francisco State University}{Expected Graduation: Dec 2020}
      {Bachelor's of Science in Computer Science}{GPA: 3.76}
      \resumeItemListStart
        \resumeItem{Coursework: }
          {Data Structures \& Analysis of Algorithms, Internet Application Design \& Development, Human-Computer Interaction, Programming Methodology, Operating System Principles}
          \resumeItem{Dean's Scholar List: }
          {Year 2016, Year 2017, Spring 2018}
      \resumeItemListEnd
\resumeSubHeadingListEnd

    
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Kandou}{San Francisco, CA}
      {Software Engineer}{Nov. 2019 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Expertise in UI/Front-End Development, developing features, and designing user interaction screens.}
        \resumeItem{}
          {Responsible for beta testing and releasing iOS and Android application to 300+ active users on app stores.}
        \resumeItem{}
          {Worked in an agile environment consisting of analyzing users and peer feedback on the submitted work.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Claryty}{San Francisco, CA}
      {Software Development Intern | Bioinformatics Research Project}{Nov. 2018 - Oct. 2019}
      \resumeItemListStart
        \resumeItem{}
          {Developed new mobile application for consumers with React Native/Redux that presents adverse effect reports for prescription drugs.}
        \resumeItem{}
          {Designed the full architecture of software stack in order to scale future Food and Drug Administration(FDA) data sets and user input.}
        \resumeItem{}
          {Involved in weekly SCRUM meetings to keep track of the ongoing project status and issues.}
        \resumeItem{}
          {Won 3rd price out of 240 projects at College of Science and Engineering annual showcase in 2019 at SF State.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Founder  - Tutoring Services}{San Francisco, CA}
      {Association of Computing Machinery at SF State}{Aug. 2017 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Consulted with students in their side projects and assignments by showing them the effective use of standard data structures and algorithms; TA for 140 hours a semester.}
        \resumeItem{}
          {Improved overall academic performance of incoming freshmen and sophomores by 30\% in core courses such as Programming Methodology and Software Development.}
        \resumeItem{}
          {Recruited, organized, and trained tutors for the Computer Science Department.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  
%-----------LEADERSHIP ACTIVITIES-----------------
\section{Leadership Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SF Hacks}{San Francisco, CA}
      {Hackathon Organizer}{Nov. 2017 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Arranged first collegiate Hackathon in San Francisco with over 350 attendees.}
        \resumeItem{}
          {Spearhead an outreach team to reach out to 30+ companies for partnership and raised \$18,000 in sponsorship.}
      \resumeItemListEnd
      
      \resumeSubheading
      {MobileSpace (React Native bootcamp)}{San Francisco, CA}
      {Teaching Assistant}{Feb. 2018 - Apr. 2018}
      \resumeItemListStart
        \resumeItem{}
          {Took initiative in learning react native and went on to successfully develop 2 functional apps under minimal supervision.}
        \resumeItem{}
          {Facilitated a dynamic and collaborative classroom of 15 students and conducted weekly office hours for further assistance.}
      \resumeItemListEnd

   \resumeSubHeadingListEnd
   
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

     \resumeSubheading
      {Facebook - Open Source}{}
      {React Native Core, React Native Website}{}
      \resumeItemListStart
        \resumeItem{}
          {Contributed in migrating ImageStore native module into the new TurboModule System architecture of the repository(v59).}
        \resumeItem{}
          {Collaborated with core contributors to comprehend the code base and get peer feedback on the submitted work.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Spiral}{}
      {Point of Sale(POS) application system with cryptocurrency wallet for local businesses}{}
      \resumeItemListStart
        \resumeItem{}
          {Designed 10+ screens to build core features of the product and shipped it within 4 weeks.}
        \resumeItem{}
          {Managed stand up meetings and assigned sprints to increase work flow throughout the team of 3 engineers.}
        \resumeItem{}
          {Used CryptoCompare API to fetch the latest cryptocurrency price for a precise transaction.}
        \resumeItem{}
          {Managed state within the app using Redux and persisted certain parts of the state to device via Redux Persist.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
    \item{
     \textbf{Languages}{: JavaScript, Java, Python, Ruby, C++, C, HTML/CSS}
    }
 \resumeSubHeadingListEnd
 \resumeSubHeadingListStart
   \item{
     \textbf{Frameworks}{: ReactJS, React Native, Redux, Node.js, Express.js}
    }
 \resumeSubHeadingListEnd
 
 \resumeSubHeadingListStart
    \item{
     \textbf{Tools}{: Git, Visual Studio Code, Developer Tools, Amazon Web Services(AWS), Firebase, Jira, Trello, Notion, Slack}
    }
 \resumeSubHeadingListEnd
 
\end{document}